---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache = FALSE)

root <- find_root("codecheck.yml")
```

```{r validate_yaml_syntax, eval=TRUE, include=FALSE}
## Validate YAML syntax - will stop rendering if YAML is invalid
validate_yaml_syntax(file.path(root, "codecheck.yml"))
```

```{r check_certificate_id, eval=TRUE, include=FALSE}
## Check if certificate identifier is set properly and try to update from GitHub
## This will check if the certificate is a placeholder and attempt to retrieve
## the actual certificate ID from GitHub issues matching the author names

# Check if certificate is a placeholder
yml_path <- file.path(root, "codecheck.yml")
if (is_placeholder_certificate(yml_path)) {
  message("CERTIFICATE ID NOT SET")

  # Try to automatically retrieve and update certificate from GitHub
  result <- update_certificate_from_github(
    yml_file = yml_path,
    issue_state = "open",
    apply_update = FALSE  # Set to TRUE to automatically update
  )

  if (!is.null(result$certificate) && result$certificate != "") {
    message("\n✓ Certificate found! To apply the update, run:")
    message("\n  update_certificate_from_github(apply_update = TRUE)")
    message("\nOr manually update codecheck.yml with certificate: ", result$certificate)
  } else {
    message("\nℹ No matching certificate found in GitHub issues.")
    message("You may need to manually set the certificate identifier in codecheck.yml")
  }
}
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r validate_certificate, echo=FALSE, results='asis'}
## Validate certificate and display warning if placeholder
## Set strict = TRUE to fail rendering if certificate is a placeholder
## Set display_warning = FALSE to suppress the warning box in PDF output
validate_certificate_for_rendering(
  yml_file = file.path(root, "codecheck.yml"),
  strict = FALSE,           # Set to TRUE to fail rendering
  display_warning = TRUE    # Set to FALSE to hide warning in PDF
)
```

```{r manifest, eval=TRUE, include=FALSE}
metadata <- codecheck_metadata(root)
manifest <- metadata$manifest

dest_dir <- file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if (!dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df <- copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
# manifest_df <- list_manifest_files(root, metadata, dest_dir)
```

```{r validate_crossref, eval=TRUE, include=FALSE, skip_on_auth_error = TRUE}
## Validate metadata against CrossRef and ORCID metadata - will fail rendering on mismatch
## Set strict = FALSE or remove this chunk if you want to skip validation
##
## ORCID validation requires authentication by default (set ORCID_TOKEN environment variable)
## If you want to skip ORCID validation when authentication is not available,
## add: skip_on_auth_error = TRUE
##
## To set up ORCID authentication:
##   1. Run: rorcid::orcid_auth()
##   2. Add ORCID_TOKEN to your .Renviron file
validation_result <- validate_contents_references(
  yml_file = file.path(root, "codecheck.yml"),
  strict = TRUE
  # Uncomment the line below to skip ORCID validation if authentication is unavailable:
  # , skip_on_auth_error = TRUE
)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This code was straightforward to codecheck.

The CODECHECK report documents the reproduction of “Improving reproducibility of GIScience publications through novel reproducibility guidelines and revised review procedures”, by Carlos Granell and colleagues, published in the Journal of Spatial Information Science (JOSIS), DOI: 10.5311/JOSIS.2026.32.591.
The computational workflow was reproduced in a local environment, and the reproduction materials and generated outputs were uploaded to a dedicated repository. All provided Quarto and Jupyter notebooks executed successfully without major computational issues.
The reproduced analyses generated all substantive results, figures, and tables reported in the published paper. The numbers of total and eligible papers in the analysed corpus matched the corresponding numbers in the paper. The descriptive results for the AGILE and GIScience conference papers, the comparisons between conferences, the hypothesis tests, the assessment-process analyses, and the authorship analyses were also successfully reproduced. Where numbering differed between the manuscript and the rendered notebooks, the underlying values and conclusions remained consistent.
All figures were reproduced exactly, although their numbering sometimes differed between the paper and the computational outputs. Figure 1 in the paper corresponded to Figure 4 in the rendered results notebook, Figure 2 corresponded to Figure 1 in the discussion notebook, and Figure 3 was reproduced as Figure 3 in the relevant rendered notebook. The pairwise group comparisons and the results discussed on pages 76–83 of the paper were likewise supported by the reproduced notebook outputs.
The reproduction instructions in the README file were clear for executing the workflow locally.

Some table cross-references in the Quarto notebooks and the CLAUDE.md file correspond to the numbering used in the preprint rather than the final published version. For example, a reproduced table described as corresponding to Table 3 actually corresponds to Table 6 in the published paper, while another described as corresponding to Table 4 corresponds to Table 7.

These discrepancies relate only to table labelling and cross-referencing, not to the computational results. Overall, all results, figures, and tables reported in the published paper were successfully reproduced.

This report includes only the figures and tables from the paper. For all other results, please refer to the rendered Quarto HTML outputs in the codecheck/outputs folder.

\clearpage

# CODECHECKER notes

```{r git_sha, echo=FALSE}
gitInfo <- get_git_info(root)
```

The reproduction was carried out on a MacBook Pro equipped with an Apple M5 processor, 32 GB of memory, and macOS Tahoe 26.5.2.
The authors’ repository was obtained from:
https://github.com/nuest/reproducible-research-giscience-longitudinal-study

The computational workflow included code written in both R and Python.
The reproduction followed these steps:

1. Cloned the authors’ reproducibility repository from GitHub.
2. Executed the Quarto and Jupyter notebooks sequentially, starting with notebook `01` and continuing through notebook `07`.

No major problems were encountered while running the workflow.
The entire CODECHECK process took approximately 60 minutes. This duration includes the additional time required because this was my first time conducting a CODECHECK. The computational reproduction itself took less time, but I am unable to provide a reliable estimate of the execution time alone.


## Recommendations

No recommendations. The code run smoothly.


\clearpage

# Manifest files

```{r manifest_files, echo=FALSE, results="asis", width=100}
render_manifest_files(manifest_df)
```

\clearpage

## Acknowledgements

I would like to thank Dr. Nüst for introducing me to the CODECHECK workflow and the other authors for providing the reproducible workflow accompanying their paper. CODECHECK is financially
supported by the Mozilla foundation.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# # handle Zenodo publication (alternative to codecheck-zenodo.R !)
# library("zen4R")
# zenodo <- ZenodoManager$new(token = zenodoToken) # assumes Zenodo token is configured via .Renviron
# record <- codecheck::get_or_create_zenodo_record(zenodo, codecheck::codecheck_metadata(root))
# record <- codecheck::upload_zenodo_metadata(zenodo, record, codecheck::codecheck_metadata(root))
# codecheck::upload_zenodo_certificate(zenodo = zenodo, record = record$id, certificate = file.path(root, "codecheck", "codecheck.pdf"))
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document")
```
